\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-14 paper/draft.tex
Update related work

In this section, we compare \sys to previously proposed systems in several categories.
For a comparison between dialysis and dynamic analysis, we refer the reader to the previous section~\sx{principles}.

% \heading{Dynamic Analysis Systems}
There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
They are also not embeddable in existing applications in a runtime-agnostic manner.
These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.

NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
NodeProf stands at a different point in the analysis design space---more powerful than \sys, but with significantly more effort.
It statically instruments the program's AST (rather than the code), making it easier to maintain compared to source changes but assuming some knowledge of the Graal and Truffle APIs and requiring recompilation of the Java hooks.
Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
Nevertheless, NodeProf's approach shares similarities with \sys, including decoupling from the source code, overheads lower than code instrumentation, and can on/off toggling during execution.
%FIXME: Lya is also limited (i) by dynamic features such as reflection, because they're gonna hit the wrapper and (ii) the equality and other primitive operators

Aran~\cite{javascript1}, an implementation sketch of proxy-based analysis, leverages JavaScript's \ttt{with} primitive to wrap custom contexts.
\sys works at the module boundaries (at a potentially coarser granularity) without any special language constructs.

JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
It allows users to write access control contracts, policies that execute at runtime.
It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.

\heading{Dynamic Analysis for WebAssembly}
Related to JavaScript is WebAssembly, a standardized subset of JavaScript target, designed to serve as a compilation target.
The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of the same goals with \sys---\eg lowering the effort required to write analyses, and providing hooks for observation rather than manipulation.
Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
  Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
  whereas our explicit goal is to write analysis in the same language as the program~\sx{goals}---that is, dialysis implemented for Python would be using Python abstractions.
Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.

\heading{Dynamic Instrumentation}
Dialysis is related to dynamic instrumentation frameworks~\cite{pin, valgrind} that wrap incrementally parts of the program to extract information.
Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
  \sys starts by wrapping a library during import, adding a small overhead on its loading time.
This overhead is only a small fraction of the time required to locate and load the module from disk.
However, these systems operate at a much lower level (binary) than \sys, and are not available to high-level runtime environments as a pluggable library.

DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} are systems for instrumenting JVM byte code.
These too work at a lower level than \sys,

\heading{Program Transformations}
% Add our work
Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
Moreover, AOP works on languages that were already designed to support it, whereas module dialysis is explicitly designed to bolt onto existing languages.

More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
While \sys makes extensive use of metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
% self element

\heading{Fracture and Recombination}
Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
PFR breaks up multiple programs into many components with the goal of exchanging functionality between donor-donee pairs of programs.
Contrary to PFR, dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.

@@

Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
Applications today routinely pull together hundreds of libraries, making their analysis difficult

due to the very same abstraction and modularity principles that have benefited software engineering for decades.

security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

This paper introduces \emph{module dialysis}, an approach 
corser
approach towards coarse-grained
This is achieved using a set of programmatic \emph{transformations} parametrizable by optional \emph{distribution recipes}.
These operate at module boundaries during runtime to collect profiling information, detect bottlenecked components, and dynamically separate and coalesce parts of the application.

We want to emphasize that \sys is open source, available to experiment with more applications and analyses

>>>>

The previous section~\sx{principles} offers a principles-comparison between dynamic analysis and dialysis.
This section we turn to a technical comparison of \sys to prior systems.

% \heading{Dynamic Analysis Systems}
There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot} are the most popular and feature fine-grained code-level instrumentation powerful enough to record and replay entire program executions.
This power comes at a significant inconvenience: % as they need to virtualize the entire execution environment.
  they incur 2--3 order-of-magnitude slowdown and are not embeddable in a runtime-agnostic manner.
% source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
These features are antithetical to \sys, which leverages basic programming-language primitives to insert high-performance analysis hooks completely transparently to the runtime environment.

NodeProf~\cite{javascript3} is a fine-grained dynamic analysis % atop Truffle~\cite{} and running on top of Graal.js~\cite{graal}, a Node.js-compatible runtime.
  standing at a different point in the analysis design space---more powerful than \sys, but with a significantly higher effort to use.
It instruments a program's AST (rather than the code) statically, % making it easier to maintain compared to source changes but
  limiting the use of dynamic features, assuming knowledge of the underlying Graal~\cite{graal} and Truffle~\cite{truffle} APIs, and requiring recompilation of the Java hooks.
% Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
Nevertheless, some of NodeProf's goals are similar to \sys such as lowering overheads and toggling analysis during execution.
%FIXME: Lya is also limited (i) by dynamic features such as reflection, because they're gonna hit the wrapper and (ii) the equality and other primitive operators

The Aran sketch~\cite{javascript1} proposes proxy-based analysis coupled with JavaScript's unusual \ttt{with} primitive for wrapping custom contexts.
\sys works at the module boundaries, a potentially coarser granularity, without any unusual language constructs.

JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework;
\fixme{Rather than extracting accesses, it arms developers with the ability to write access control contracts (\ie executable partial specifications)}.
This capability is complimentary to \sys's security analysis model~\sx{examples}, illustrating a need for a general-purpose online analysis framework.
% \ie their analysis can be implemented on top of \sys with significantly less effort.
% build around proxies.

JavaScript is related to WebAssembly, a standardized subset of JavaScript target designed to serve as a compilation target.
The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of \sys' goals---\eg low-effort analysis and API for observation rather than manipulation.
% Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
%   Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
%   whereas \sys's partial goal is supporting analysis in the same language as the program~\sx{goals}. % ---that is, dialysis implemented for Python would be using Python abstractions.
Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims for heavyweight instrumentation.

\sys has some resemblance to dynamic instrumentation frameworks~\cite{pin, valgrind, disl, roadrunner}.
These wrap basic blocks of a program incrementally and right before execution, similar in vein to how \sys wraps libraries.
% Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
%   \sys starts by wrapping a library during import, adding a small overhead on its loading time.
However, they operate at a much lower level (binary) than \sys, are much more detailed and heavy-weight, and are not available to high-level runtime environments as a language-aware library.

% Add our work
Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
Moreover, AOP works on languages that were already designed to support it, whereas module dialysis is explicitly designed to bolt onto existing languages.

More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
While \sys uses metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
% self element

Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
PFR breaks up multiple programs into many components with the goal of exchanging functionality between donor-donee pairs of programs.
Contrary to PFR, dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.

@@

Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
Applications today routinely pull together hundreds of libraries, making their analysis difficult.
To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
% is a general technique that
Contrary to heavy-weight dynamic analysis that provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand, dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.

We note that \sys is open source, available for experimentation with other applications and analyses.
